Peaks Over Threshold for Bursty Time Series

### 2018-04-16 article_springer/article_springer.Rmd
Simplify section on scaling limit of exceedance time

@@

: Let $b(c)$ be the scaling function \eqref{eq:bScale},
and let $\ell$ be a threshold from the support $[x_L, x_R]$ of $J$. 
Furthermore let $p := \mathbf P(J > \ell)$. Under the assumption \eqref{eq:Wscale} and the assumptions of the GEV Theorem, we have 
\begin{equation} \label{eq:Tellscale}
T(\ell) / b(1/p) \to {\rm ML}(\beta, 1) \text{ as } \ell \uparrow x_R.
\end{equation}

@@

```{r make-caption}
caption = "
Tail and scale estimates for simulated data, with waiting times drawn from 
the stable distribution $S_\\beta(\\cos(\\pi \\beta/2)^{1/\\beta}, +1, 0)$ 
with $\\beta = 0.8$. Dashed lines are 95\\% 
confidence intervals, dotted 
lines are the known theoretical values ($0.8$ and $10000^{1/0.8}$).
\\label{fig:sim}
"
```

@@

The Mittag-Leffler distribution with parameter $\beta \in (0,1]$ is 
a heavy-tailed positive distribution if $\beta < 1$; for $\beta = 1$, 
it specializes to the Exponential distribution. 
For $\sigma > 0$, we write ${\rm ML}(\beta, \sigma)$ for the distribution 
of $\sigma Y$, where $Y$ has Laplace transform 
$\mathbf E[\exp(-s Y)] = 1/(1+s^\beta)$. Due to e.g. Theorem 19.1 in 
@Haubold11, the exceedance time from Theorem MS2 can be written as 
\begin{align} \label{eq:hitting-ML}
B(\ell^*) \sim {\rm ML}\left(\beta, (-\log F_A(\ell^*))^{-1/\beta}\right)
\end{align}

>>>>

In this section we state the key theorem below (a proof is in the appendix). 
For more details on regular variation and stable limit theorems, we 
recommend the book by @MeerschaertSikorskii.

@@

: Let the waiting times $J_k$ be in the domain of attraction of a 
positively skewed sum-stable law with stability parameter $0 < \beta < 1$; 
more precisely,
$$
\frac{W_1 + \ldots + W_n}{b(n)} \overset{d}{\longrightarrow} D, 
\quad n \to \infty
$$
for a function $b(n)$ which is regularly varying at $\infty$ with 
parameter $1/\beta$, and where $\mathbf E[\exp(-sD)] = \exp(-s^\beta)$. 
Write $p := \mathbf P(J > \ell)$. Then the weak convergence
$$
\frac{T(\ell)} {b(1/p)} \to W_\beta \quad \text{ as } \quad \ell \uparrow x_R
$$
holds, where the Mittag-Leffler random variable $W_\beta$ is defined on 
the positive real numbers via 
$$
\mathbf E[\exp(-sW_\beta)] = \frac{1}{1+s^\beta}.
$$

\noindent In general, for $\sigma > 0$ we write ${\rm ML}(\beta, \sigma)$ for the 
distribution of $\sigma W_\beta$. 
The Mittag-Leffler distribution with parameter $\beta \in (0,1]$ is 
a heavy-tailed positive distribution for $\beta < 1$, with infinite mean. 
However, as $\beta \uparrow 1$, ${\rm ML}(\beta, \sigma)$ converges 
weakly to the exponential distribution ${\rm Exp}(\sigma)$.
This means that although its moments are all infinite, the Mittag-Leffler
distribution may (if $\beta$ is close to 1) be indistinguishable from the 
exponential distribution, from the point of view of applied statistics. 
For a detailed reference on the Mittag-Leffler distribution, see e.g. 
@Haubold11.

@@

```{r make-caption}
caption = "Tail and scale estimates for simulated data, with waiting times drawn from the stable distribution $S_\\beta(\\cos(\\pi \\beta/2)^{1/\\beta}, +1, 0)$ with $\\beta = 0.8$. Dashed lines are 95\\% confidence intervals, dotted lines are the known theoretical values ($0.8$ and $10000^{1/0.8}$). \\label{fig:sim}"
```

@@
